\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-07-30 manuscript/Rmd/draft.Rmd

For our analysis on the relationship between the rankings of the events and the final result, we used data from the 2018 Youth Olympics Women's Qualification. Figure 2 is a scatterplot and correlation matrix between the ranks of the individual events and the final standings, with Kendall’s Tau [@kendall1938] as our measure of ordinal association between the quantities. It is evidently clear that there exists a strong and positive correlation between the ranks of bouldering and lead climbing, and as a results, the standings of these two events are highly correlated with the final rankings. On the other hand, the correlation with the final rank is not as strong for speed climbing. Thus, speed climbers are facing a huge disadvantage in this scoring system, compared to those that are specialized in the other two concentrations. This trend also holds for most of the past competitions. (add table to the appendix)

>>>>

For our analysis on the relationship between the rankings of the events and the final result, we used data from the 2018 Youth Olympics Women's Qualification. Figure 2 is a scatterplot and correlation matrix between the ranks of the individual events and the final standings, with Kendall’s Tau [@kendall1938] as our measure of ordinal association between the quantities. It is evidently clear that there exists a strong and positive correlation between the ranks of bouldering and lead climbing, and as a results, the standings of these two events are highly correlated with the final rankings. On the other hand, the correlation with the final rank is not as strong for speed climbing as the other two events. Thus, speed climbers are facing a huge disadvantage in this scoring system, compared to those that are specialized in the other two concentrations. This validates the concerns of climbers in the interview mentioned in Section \ref{introduction}

This trend also holds for most of the past competitions. (add table to the appendix)

### 2021-07-30 manuscript/Rmd/draft.tex
Update Rmd

  \author{
        Quang Nguyen \\
    LUC\\
     and \\     Hannah Butler \\
    CSU\\
     and \\     Gregory Matthews \\
    LUC\\
      }
  \maketitle
} \fi

@@

For our analysis on the relationship between the rankings of the events
and the final result, we used data from the 2018 Youth Olympics Women's
Qualification. Figure 2 is a scatterplot and correlation matrix between
the ranks of the individual events and the final standings, with
Kendall's Tau \citep{kendall1938} as our measure of ordinal association
between the quantities. It is evidently clear that there exists a strong
and positive correlation between the ranks of bouldering and lead
climbing, and as a results, the standings of these two events are highly
correlated with the final rankings. On the other hand, the correlation
with the final rank is not as strong for speed climbing. Thus, speed
climbers are facing a huge disadvantage in this scoring system, compared
to those that are specialized in the other two concentrations. This
trend also holds for most of the past competitions. (add table in the
appendix)

>>>>

  \author{
        Quang Nguyen \\
    \textit{Loyola University Chicago}\\
     and \\     Hannah Butler \\
    \textit{Colorado State University}\\
     and \\     Gregory J. Matthews \\
    \textit{Loyola University Chicago}\\
      }
  \maketitle
} \fi

@@

For our analysis on the relationship between the rankings of the events
and the final result, we used data from the 2018 Youth Olympics Women's
Qualification. Figure 2 is a scatterplot and correlation matrix between
the ranks of the individual events and the final standings, with
Kendall's Tau \citep{kendall1938} as our measure of ordinal association
between the quantities. It is evidently clear that there exists a strong
and positive correlation between the ranks of bouldering and lead
climbing, and as a results, the standings of these two events are highly
correlated with the final rankings. On the other hand, the correlation
with the final rank is not as strong for speed climbing as the other two
events. Thus, speed climbers are facing a huge disadvantage in this
scoring system, compared to those that are specialized in the other two
concentrations. This validates the concerns of climbers in the interview
mentioned in Section \ref{introduction}

This trend also holds for most of the past competitions. (add table to
the appendix)
